\hypertarget{backend-nlp-engineer}{%
\section{BackEnd NLP engineer}\label{backend-nlp-engineer}}

\hypertarget{summary}{%
\subsection{Summary}\label{summary}}

\begin{itemize}
\tightlist
\item
  Full name: Vadim Polulyakh
\item
  Experience: 10 years
\item
  City: Moscow
\end{itemize}

\hypertarget{core-skills}{%
\subsection{Core skills}\label{core-skills}}

Scala, SciPy, TensorFlow, Natural Language Processing, Natural Language
Toolkit (NLTK), Akka, Play Framework, pandas, Apache Spark, Chatbot
Development.

\hypertarget{projects}{%
\subsection{Projects}\label{projects}}

I have developed some projects from scratch. You can estimate my
practical skills on them:

\begin{itemize}
\tightlist
\item
  \url{https://declaration.fastlaw.io} is a service for the quick
  creation of Tax returns. This service uses AI technologies to extract
  information from photos. You just need to upload photos of your
  documents, answer a couple of questions and wait for the system to
  create all the necessary documents. This software helps you to save
  about 50 minutes on a Tax return. Technological stack: scala,
  typescript, python, tensorflow.
\item
  \href{smartnalog.ru}{http://smartnalog.ru} is a knowledge base on
  Russian tax law developed by me from scratch in 3 months. The main
  challenge of the project was the development of a search engine. This
  search engine uses AI technologies (fasttext, WMD) to select an
  article from knowledge base that is appropriate for the user's
  question. The question is forwarded to the lawyer if no article is
  found. This answer is remembered. Thus, I managed to create a database
  of answers in two months. Technological stack: python, typescript,
  tensorflow.
\end{itemize}

\hypertarget{work-history}{%
\subsection{Work history}\label{work-history}}

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.22\columnwidth}\raggedright
employment period\strut
\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedright
name of organization\strut
\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedright
position\strut
\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedright
duties/achievements\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2017 --- 2020\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
\href{http://ipavlov.ai/}{DeepPavlov}\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
chief engineer\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
We were developing an open-source framework for building chatbots. Our
framework includes state-of-the-art NLP models. I lead the department
creating the final solutions based on the framework.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2015 --- 2017\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
\href{https://www.raiffeisen.ru}{Raiffeisen Bank}\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
senior lead developer\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
I have been engaged in the development of mission-critical services:
authorization, monitoring, and data storage.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2012 --- 2015\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
\href{https://ediweb.com}{Edisoft Development ltd.}\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
system architect\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Head of the research, development and prototyping architecture of
electronic document interchange services.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2011 --- 2012\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
\href{http://www.acronis.com}{Acronis ltd.}\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
software engineer\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Participated in the development of Acronis Backup and Recovery for Linux
as a regular developer. Moreover, I was a release manager and manage
codebase of Acronis Backup and Recovery project (\textasciitilde90GB in
SVN repo).\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2008 --- 2010\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
\href{https://mpei.ru/lang/en/Pages/default.aspx}{Moscow Power
Engineering Institute}\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
developer\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Participated in the development software for the Russian Ministry of
Education.\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{longtable}[]{@{}lll@{}}
\toprule
year of graduation & school & degree\tabularnewline
\midrule
\endhead
2010 & Moscow Power Engineering Institute & Masters Degree in Computer
Science\tabularnewline
2011 & \href{https://www.udacity.com}{udacity.com} & Artificial
Intelligence\tabularnewline
2012 & \href{https://www.coursera.org}{Coursera.org} & Software
Engineering for SaaS\tabularnewline
2013 & \href{https://www.udacity.com}{udacity.com} & Artificial
Intelligence for Robotics\tabularnewline
2014 & \href{https://www.coursera.org}{Coursera.org} & Machine
Learning\tabularnewline
2014 & \href{https://www.coursera.org}{Coursera.org} & Functional
Programming Principles in Scala\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{about-me}{%
\subsection{About me}\label{about-me}}

I am an experienced engineer who has created several large projects from
scratch. I will be glad to help you if you need a rapid prototype of an
AI-based web service, to solve a practical natural language processing
task or to set up a machine learning pipeline.

\hypertarget{contacts}{%
\subsection{Contacts}\label{contacts}}

\begin{itemize}
\tightlist
\item
  email: \href{mailto:bavadim@gmail.com}{\nolinkurl{bavadim@gmail.com}}
\item
  web-site: \url{http://bavadim.me}
\item
  github: \url{https://github.com/bavadim/}
\end{itemize}
